\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2021-03-28 paper.tex
Updated split_url definition
rewording future work

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}" is a string that represents the type of the video
  \item "\texttt{url}" is the url that the video was fetched from
  \item "\texttt{is\_split\_url}" is a boolean that represents if all of the frames of the video have bounding boxes in this metadata
  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{collision\_locations}" a list of frames indicating the collisions
  \item "\texttt{bb\_fields}" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
  \begin{itemize}
    \item "\texttt{ids[i]}" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
    \item "\texttt{class[i]}" represents the object class of the vehicle
    \item "\texttt{frames[i]}" represents what frame of the video the $i_{th}$ bounding box is for
    \item "\texttt{has\_collision[i]}" represents if the vehicle with id \texttt{ids[i]} is in a collision
    \item "\texttt{x1s[i], y1s[i], x2s[i], y2s[i]}" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box i
  \end{itemize}
\end{itemize}`

@@

There are many ways that we could improve on our system. This are just a series of ideas that we could think of:
\begin{enumerate}
\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames. Currently, linear interpolation is always used. Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered. While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.

>>>>

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}" is a string that represents the type of the video
  \item "\texttt{url}" is the url that the video was fetched from
  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{collision\_locations}" a list of frames indicating the collisions
  \item "\texttt{bb\_fields}" contains all bounding-box specific data. Each entry is a list, where the $i_{th}$ index in each contains the data for one bounding-box:
  \begin{itemize}
    \item "\texttt{ids[i]}" represents what vehicle id the $i_{th}$ bounding box represents. Each vehicle in the video has it's own unique id
    \item "\texttt{class[i]}" represents the object class of the vehicle
    \item "\texttt{frames[i]}" represents what frame of the video the $i_{th}$ bounding box is for
    \item "\texttt{has\_collision[i]}" represents if the vehicle with id \texttt{ids[i]} is in a collision
    \item "\texttt{x1s[i], y1s[i], x2s[i], y2s[i]}" are the coordinates of the two points $(x_1,y_1)$ \& $(x_2,y_2)$ that make bounding box i
  \end{itemize}
\end{itemize}`

@@

There are many ways that we could improve our system, such as the following:
\begin{enumerate}
\item Custom interpolation between input frames: One idea would be to make it easier to modify the method of interpolation between frames. Currently, linear interpolation is always used. Moreover, given a type of interpolation is stored in the metadata, we probably shouldn't store all interpolated frames, rather than just the ones the user has entered. While linear interpolation works great for entering a frame every 10 frames, supporting more interpolations could be great for faster data entry, or even for supporting affine transformations on more complex bounds.
